\documentclass[margin,line, 11pt]{res}

\topmargin=-0.5in    % Make letterhead start about 1 inch from top of page
\textheight=10in  % text height can be bigger for a longer letter
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in

\nofiles

% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\renewcommand{\familydefault}{\sfdefault}
%\usepackage[sfdefault, light, condensed]{roboto}
\usepackage[light,condensed]{iwona}
\usepackage[T1]{fontenc}
\usepackage[colorlinks=false,urlcolor=magenta,citecolor=blue,linkcolor=blue]{hyperref}

\begin{document}

\name{{\huge\bf Steven Boada, Ph.D}\vspace*{.1in}}

\begin{resume}
\vspace*{-2mm}
\section{Basic\\Information}
\begin{tabular}{@{}p{4.9in}p{4in}}
  (615) 200-0119 & \href{https://github.com/boada}{github.com/boada} \\
  \href{mailto:stevenboada@gmail.com}{stevenboada@gmail.com} & \href{https://linkedin.com/in/theboada}{linkedin.com/in/theboada} \\
\end{tabular}

% \vspace{-3mm}
% Collaborative, scientific thinker passionate about discovering and communicating nuanced insight from complicated data. Background includes: open-source contributions, project leadership, computer vision, traditional machine learning, and working with large, heterogeneous, often noisy datasets.
% \vspace*{-2mm}

\section{Professional \newline Experience}
\textbf{Activision Publishing, Inc.} \hfill Boulder, Colorado\newline
\textit{Senior Machine Learning Engineer} \hfill \textbf{January, 2021 - Present}\newline
As part of the Advanced Analytics and Machine Learning (ML) team, I support all ML initiatives for the Call of Duty and Warzone franchises. This includes being involved in early concept designs through the productionalization of mature models and stakeholder management. Below are selected highlights from this very diverse role:
    \begin{list2}
%     	\vspace*{-5mm}
      \item Designed, built, maintained, and improved ML infrastructure. This includes tool developement like autoML, CI/CD (Jenkins), model tracking and management (MLflow) and orchestration (Airflow).
      \item Crafted and implimented policy around external data ingestion and data product retention for both my internal team and for sharing across the organization.
      \item Designed, built, and maintained near-realtime applications to combat in-game cheating and other malicious behavior. Typical time-to-action is in the low 10s of seconds.
      \item Lead the transition of ML infrastructure from AWS to GCP/GCS.
      \item Created ML models to provide insights into customer conversion, churn, and behavioral segmentation. This leveraged survival analysis, clustering, as well as tree-based and linear methods.
      \item Supervised junior team members to design and develope recommendation systems to be productionalized in a future title. 
    \end{list2}
\vspace*{-2mm}

\textbf{Insight Data Science} \hfill New York, New York\newline
\textit{Fellow} \hfill \textbf{January, 2020 - 2021}\newline
    \begin{list2}
    	\vspace*{-5mm}
      \item Helped optimize the way NYC health inspectors perform restaurant inspections in order to reduce the time critical health violations remain unaddressed.
    	\item Trained a random forest in Python to prioritize NYC restaurant inspections based on environmental variables and their past inspection histories and provided the results to NYC through an API deployed on AWS.
    	\item Resulted in NYC inspectors identifying $\sim$2.5\% more violations in the first half of an inspection window,  leading to critical violations being discovered up to 7 days earlier than by the current approach implemented by NYC.
    \end{list2}
\vspace*{-2mm}

\textbf{Dept. of Physics and Astronomy, Rutgers University} \hfill New Brunswick, New Jersey\newline
\textit{Postdoctoral Research Associate} \hfill \textbf{September, 2016 - 2021}\newline
    \begin{list2}
    	\vspace*{-5mm}
    	\item Designed and built parallelized pipelines to process and analyze TBs of astronomical imaging; producing calibrated, standardized data catalogs and rigorous results leading to 2 peer reviewed publications and several hundred hours of telescope time.
    	\item Project managed and coordinated a team of 4, including both senior scientists and graduate students,
      to perform quality control tasks; deliver science products; and produce peer-reviewed publications.
    	\item Contributed to open source, astronomy-focused, Python projects through bug fixes and feature additions: see \href{https://github.com/boada/photometrypipeline}{photometrypipeline}, \href{http://astlib.sourceforge.net/}{astLib}, and \href{https://github.com/boada/easyGalaxy}{easyGalaxy} on GitHub as examples.
    \end{list2}
\vspace*{-2mm}

% \textbf{Dept. of Physics and Astronomy, Texas A\&M University} \hfill College Station, Texas\newline
% \textit{Ph.D Candidate} \hfill \textbf{August, 2010 - 2016}\newline
%     \begin{list2}
%     	\vspace*{-5mm}
%       \item Demonstrated that measurements from a planned large observation campaign could be improved by up to a factor of 3 over traditional statistical methods through the use of machine learning.
%       \item Implemented these machine learning methods and produced reliable results in a pilot survey of the real sky and under real-world conditions.
%     	% \item Collaborated with group members both in person, and through collaborative tools (e.g., GitHub, SVN).
%     	% \item Presented scientific results in high-impact, astrophysical journals and at international conferences.
%     \end{list2}
% \vspace*{-2mm}

% \textbf{The University of Tennessee}, Knoxville, Tennessee USA\newline
% \textit{Master's Candidate} \hfill \textbf{August, 2007 - 2009}\newline
%     \begin{list2}
%     	\vspace*{-5mm}
%       \item Implemented a C-based pipeline to process hundreds of GBs of simulation results. Including a computer vision algorithm to automatically analyze and compare results to expected targets.
%       \item Optimized simulation parameters using a genetic algorithm based search utilizing HPC (100k+ core) systems at the National Center for Computational Science, part of Oak Ridge National Laboratory
%     \end{list2}
% \vspace*{-3mm}

% \section{Awesome Projects}
% \textbf{Using Imaging to Infer Galaxy Properties}\newline
%     \begin{list2}
%     	\vspace*{-5mm}
%       \item Predicted galaxy chemical composition with $\sim$5\% error from pseudo-three color imaging, a result better than other current, similar efforts in the literature. Leveraged CNNs to analyze $\sim$150,000 images of galaxies.
%       \item Project start to publication: 4 months (typically $\sim$1.5 years). See: \href{https://github.com/boada/galaxy-cnns}{github.com/boada/galaxy-cnns}.
%     \end{list2}
%     \vspace*{-3mm}

% \textbf{Predicting Tournament Performance in Warmachine}\newline
%     \begin{list2}
%     	\vspace*{-5mm}
%     	\item Created an \href{https://en.wikipedia.org/wiki/Elo_rating_system}{Elo} based model to forecast the results of upcoming tournaments and identify potential upsets.
%     	\item Integrated predictions into a local community ranking system and forecasted $\sim$1800 tournament game results of the popular tabletop game using Python (e.g., Pandas).
%     \end{list2}
% \vspace*{-1mm}

\section{Skills}
\textbf{Machine Learning:} Linear Models, Decision Trees, SVM, Clustering, Deep Learning, Survival Analysis\\
\textbf{CI/CD:} Jenkins, Airflow, Docker\\
% \textbf{Statistical Methods:} Hypothesis testing, error analysis, Monte Carlo methods, maximum likelihood\\
\textbf{Software and Computing:} Open Source Contributor, Python, DataBricks, MLFlow, SQL, AWS/GCP, and other cloud computing applications \\
\textbf{Leadership:} Experience organizing and leading workshops and collaboration meetings, Teaching and mentoring junior team members, Eagle Scout. \\
\vspace*{-7mm}

%section for two column education
\section{Education}
\begin{tabular}{@{}p{3in}p{3in}}
  \textbf{Texas A\&M University}, College Station, Texas
  \begin{list2}
  	\item Ph.D, Physics (astronomy focus), 2016
  \end{list2} &
  \textbf{The University of Tennessee}, Knoxville, Tennessee
  \begin{list2}
  	\item M.S., Physics (astronomy focus), 2009
  	\item B.S., Physics, 2007
  \end{list2} \\
\end{tabular}
\vspace*{-4mm}

\end{resume}
\end{document}
